EvoSwarm: An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-05-06 draft.tex
listings

\graphicspath{ {./images/} }

@@

@@

@@

% This is the second level? - JJ
Algorithm developers can upload the container definition or images directly to
DockerHub; another option is to upload the container image definition (Dockerfile) to
GitHub and define a trigger to re-upload the image to DockerHub; this
can be defined in DockerHub (or any other registry) too.u 
% This is probably accessory. What difference would it make to upload it to GitHub?
% You also need to say in this section how it helps your overall objective. Does it contribute to reproducibility? We've talked about that elsewhere. Does it help diversity by making easy to add new algorithms? - JJ

>>>>

\lstset{
basicstyle=\small\ttfamily,
}
\graphicspath{ {./images/} }

@@

\begin{lstlisting}[language=Python, caption=Python example]
{"problem":{
  "name":"BBOB","instance": 1,"error":1e-8,"function":4,
  "dim":3,"search_space":[-5,5],
  "problem_id":"1515-4-1-3",
  "max_iterations": 20,"population":[],
  "population_size": 100,
  "algorithm": "GA",  
  "params":{
      "GA":{"crossover": { "type": "cxTwoPoint", 
            "CXPB_RND": [0.2, 0.6], "CXPB": 0.26},
             "mutation": { "MUTPB_RND": [0.1, 0.3], 
             "indpb": 0.05, "sigma": 0.5, 
             "type":"mutGaussian","mu":0,"MUTPB":0.12},
             "selection": { 
               "type": "tools.selTournament", 
               "tournsize": 2 },
               "iterations": 50},
       "PSO": {"Vmax":5,"wMax":0.9,"wMin":0.2,
               "c1":2,"c2":2,"iterations":50 } 
    },
  "experiment":{"type":"benchmark","experiment_id": 1515}
  }
}
\end{lstlisting}

@@

\begin{lstlisting}[language=Python, caption=Python example]
{
"time_stamp": 1588455316.698875,
"evals": [
  {
    "gen_num": 0, "best_fitness": -259.96925945939404,
    "best_solution": [ -4.9446848321611405, 
                        2.593007989886873, 
                        2.0011025031167673],
    "num_of_evals": 17
  },
  {
    "gen_num": 49, "best_fitness": -419.47555780783347,
    "best_solution": [ -0.9165294450108963, 
                        2.291966676472422, 
                        1.8527006568795485],
    "num_of_evals": 28
  }
],
"worker_id": "4f5eb12e-8278-40de-b0f3-4ac18171566d",
"message_counter": 1,
"message_id": "cbcd2e82-e232-4818-8aec-2cd072c7cfe9",
"best_score": -419.47555780783347
}
\end{lstlisting}

@@

% This is the second level? - JJ
Algorithm developers can upload the container definition or images directly to
DockerHub; another option is to upload the container image definition (Dockerfile) to
GitHub and define a trigger to re-upload the image to DockerHub; this
can be defined in DockerHub (or any other registry) too.u 
% This is probably accessory. What difference would it make to upload it to GitHub?
% You also need to say in this section how it helps your overall objective. Does it contribute to reproducibility? We've talked about that elsewhere. Does it help diversity by making easy to add new algorithms? - JJ
\begin{lstlisting}[language=Python, caption=Python example]
{
 "DIM_CONFIGURATION" : 
 {
 "2":{"GEN":40,"POP_SIZE": 50,"MAX_ITER":10,"MESSAGES":10},
 "3":{"GEN":25,"POP_SIZE": 60,"MAX_ITER":20,"MESSAGES":10},
 "5":{"GEN":28,"POP_SIZE": 60,"MAX_ITER":30,"MESSAGES":10},
"10":{"GEN":50,"POP_SIZE": 70,"MAX_ITER":30,"MESSAGES":10},
"20":{"GEN":66,"POP_SIZE":100,"MAX_ITER":30,"MESSAGES":10},
"40":{"GEN":80,"POP_SIZE":125,"MAX_ITER":40,"MESSAGES":10}
},
"GA_WORKER_RATIO" : 0.5,
"FUNCTIONS": [4],
"DIMENSIONS" : [2, 3, 5, 10, 20, 40],
"CXPB_RND": [0.2, 0.6],
"MUTPB_RND": [0.1, 0.3]
}
\end{lstlisting}
